Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-07-25 main.tex
Update on Overleaf.

@@

\begin{proof}
    \begin{itemize}
    \item 
    Consider any simplex $T$ with one vertex $v_0$ at the origin. 
    Let $\lambda_{0}, \lambda_{1}, \dots, \lambda_{n}$ be the barycentric coordinates. 
    The mapping 
    \begin{align}
        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
    \end{align}
    maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
    On the one hand, by the reverse triangle inequality,
    \begin{align}
        \left| F(x) - F(y) \right|
        &\geq 
        \left\| 
            \frac{x}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \frac{y}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right\|
        \\&
        \geq 
        \left| 
            \frac{\|x\|}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \frac{\|y\|}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right|
        \\&
        = 
        \left| 
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right|
        \\&
        = 
        \left| 
            \vec{1}
            \cdot 
            A^{-1}( x - y )
        \right|
     \end{align}
     Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$.

    \item 
    We let $S^{n}_{\star} := S^{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
    Suppose that $\bar x \in S^n$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
    We define its stereographic projection as 
    \begin{align}
        \pi( \bar x ) 
        = 
        \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
        .
    \end{align}
    This is a mapping $\pi : S^{n}_{\star} \rightarrow \bbR^{n}$. 
    Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
    \begin{align}
        \pi^{-1}( y )
        = 
        \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
        +
        \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
        .
    \end{align}
    \item 
    Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
    \begin{align}
        \mu : \bbR^{n} \rightarrow \bbR^{n},
        \qquad 
        y \mapsto \frac{y}{\| y \|}.
    \end{align}
    \item 
    \begin{align}
        G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
    \end{align}
    \item 
    \begin{align}
        F^{-1} \pi^{-1} G^{-1} \mu G \pi F
    \end{align}
    \end{itemize}
\end{proof}

>>>>

\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}
    \item 
    We use the following auxiliary lemma. Suppose that $\|\cdot\|_{\alpha}$ and $\|\cdot\|_{\alpha}$ are two norms on a Banach space.
    Let 
    $$
        F_{\alpha,\beta}(x) = \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} }.
    $$
    Then 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        C_{\beta}^{\alpha} 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
        \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        \left\| 
            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
            \| x \|_{\alpha}
            \| y \|_{\alpha}
        C_{\beta}^{\alpha} 
        \frac{ \| y \|_{\alpha} }{ \| y \|_{\beta} } 
        \left\| x - y \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        C_{\alpha}^{\beta} 
        \left\| x - y \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        C_{\alpha}^{\beta} 
        \left\| x - y \right\|_{\alpha}
        \| 
            F(x) - F(y) 
        \|_{\beta}
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
        \right\|_{\beta}
        \left\| 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
        \right\|_{\beta}
        \left\| 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| 
            x - y
        \right\|_{\beta}
        \frac{ \| y \|_{\beta} }{ \| x \|_{\beta} } 
        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
        \| y \|_{\alpha} \| y \|_{\beta} 
            \frac{ 1 }{ \| x \|_{\beta} } 
            \frac{ 1 }{ \| y \|_{\beta} }  
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| 
            x - y
        \right\|_{\beta}
        % BEcause w l o g 
        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
        \| y \|_{\alpha} \| y \|_{\beta} 
        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| 
            x - y
        \right\|_{\beta}
        % BEcause w l o g 
        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
        \| y \|_{\alpha} \| y \|_{\beta} 
        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| x - y \right\|_{\beta}
        % BEcause w l o g 
        \left\| x - y \right\|_{\alpha}
        \| y \|_{\alpha} \| y \|_{\beta} 
        \frac{ \left\| x - y \right\|_{\beta} }{ \| y \|_{\beta} \| y \|_{\beta} }
        C^{\alpha}_{\beta} 
        C^{\beta}_{\alpha}
        \left\| x - y \right\|_{\alpha}
        % BEcause w l o g 
        \left\| x - y \right\|_{\alpha}
        C^{\alpha}_{\beta} 
        C^{\beta}_{\alpha}
        \left\| x - y \right\|_{\alpha}
    \item 
    Consider any simplex $T$ with one vertex $v_0$ at the origin. 
    Let $\lambda_{0}, \lambda_{1}, \dots, \lambda_{n}$ be the barycentric coordinates. 
    The mapping 
        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right) = \frac{x}{\|x\|} \left( 1 - \lambda_{0}(x) \right)
    maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
    On the one hand, 
        F(x) - F(y)
        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{y}{\|y\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
    Without loss of generality, $\|y\| \leq \|x\|$. 
        \left\| F(x) - F(y) \right\|
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
        \left\| x - y \right\|
        \sqrt{n} \sigma_{\min}(A^{-1})
        \sqrt{n} \sigma_{\min}(A^{-1}) \left\| x - y \right\|
        \left\| x - y \right\|
        \sqrt{n} \sigma_{\min}(A^{-1})
        3\sqrt{n} \sigma_{\min}(A^{-1})
        \left\| x - y \right\|
        \left\| F(x) - F(y) \right\|
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \left| \|y\| - \|x\| \right| }{\|x\|}
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \| x - y \| }{\|x\|}
        \left\| x - y \right\|
        \frac{ \lambda_{0}(x) }{\|x\|}
        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
        \left( \lambda_{0}(y) \right)
        \frac{ \| x - y \| }{\|y\|}
    On the one hand,
    we compute the Jacobian  
        \Jacobian F(x) 
        \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
        \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \nabla\lambda_{i}(x) \right)
    On the other hand, by the reverse triangle inequality,
        \left| F(x) - F(y) \right|
        &\geq 
        \left\| 
            \frac{x}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            \frac{y}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right\|
        \geq 
            \frac{\|x\|}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            \frac{\|y\|}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
            \sum_{i=1}^{n} \lambda_{i}(x)
            \sum_{i=1}^{n} \lambda_{i}(y)
            \vec{1}
            A^{-1}( x - y )
    Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$. 
        \left| F(x) - F(y) \right|
        &\geq 
        \left\| 
            \frac{x}{\|x\|}
            \left( 1 - \lambda_{0}(x) \right) 
            \frac{y}{\|y\|}
            \left( 1 - \lambda_{0}(y) \right) 
        \right\|
        \geq 
        \left\| 
            \frac{x}{\|x\|}
            \left( 1 - \lambda_{0}(x) \right) 
            \frac{y}{\|y\|}
            \left( 1 - \lambda_{0}(y) \right) 
        \right\|
    \todo{finish this estimate somehow}

    \item 
    We let $S^{n}_{\star} := S^{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
    Suppose that $\bar x \in S^n$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
    We define its stereographic projection as 
    \begin{align}
        \pi( \bar x ) 
        = 
        \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
        .
    \end{align}
    This is a mapping $\pi : S^{n}_{\star} \rightarrow \bbR^{n}$. 
    Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
    \begin{align}
        \pi^{-1}( y )
        = 
        \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
        +
        \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
        .
    \end{align}
    \item 
    Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
    \begin{align}
        \mu : \bbR^{n} \rightarrow \bbR^{n},
        \qquad 
        y \mapsto \frac{y}{\| y \|}.
    \end{align}
    \item 
    \begin{align}
        G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
    \end{align}
    \item 
    \begin{align}
        F^{-1} \pi^{-1} G^{-1} \mu G \pi F
    \end{align}
    \item 
    We use the following result~\cite[Theorem~3]{alestalo2018radial}:
    if $f : S \rightarrow S$ is an $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
    then the radial extension $f : B \rightarrow B$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
    \end{itemize}
\end{proof}

% Please cite the original version:
% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant

@@
